% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{url}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Alexander Pak}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{0.6em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
	Mailing address:\\
	52 rue du Faubourg Poissonniere \\
	Paris 75010, France
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone: & (+33) 0670655238 \\
    Email: & \href{mailto:alexpak@limsi.fr}{\tt alexpak@limsi.fr}\\
	       & \href{mailto:irokez@gmail.com}{\tt irokez@gmail.com}
  \end{tabular}
\end{minipage}

\section*{Personal}

\begin{itemize}
\item Birthday: July 10, 1986.
\item Nationality: Uzbekistan
\end{itemize}


\section*{Employment}

\begin{table}[h]
	\begin{tabular}{ll}
	\parbox[t]{5cm}{
		Sep 2012 -- current \\
		full time
	} &
	\parbox[t]{15cm}{
		Google \\
		Software engineer
		\vspace{1em}
    } \\
	\parbox[t]{5cm}{
		May 2007 -- Aug 2007 \\
		full time
	} &
	\parbox[t]{15cm}{
		Center of Economic Research \\
    	United Nations Development Programme Project (UNDP)\\
		IT coordinator
		\vspace{1em}
    } \\
	\parbox[t]{5cm}{
		Mar 2006 -- May 2007 \\
		contract work
	} &
	\parbox[t]{15cm}{
		Center of Economic Research \\
    	United Nations Development Programme Project (UNDP)\\
		Software developer
		\vspace{1em}
    } \\
    \parbox[t]{5cm}{
		Dec 2005 -- Mar 2006\\
		part-time
	} &
	\parbox[t]{15cm}{
		Erava Group LLC\\
		Project manager
		\vspace{1em}
    } \\    
    \parbox[t]{5cm}{
		Jun 2004 -- Dec 2005\\
		part-time
	} &
	\parbox[t]{15cm}{
		Erava Group LLC\\
		Software developer
    } \\
    \end{tabular}
\end{table}

\section*{Education}

\begin{table}[h]
	\begin{tabular}{ll}
	\parbox[t]{5cm}{
		2009 -- 2012 \\
		Ph.D. Computer Science
	} &
	\parbox[t]{15cm}{
    	University Paris-Sud 11\\
		LIMSI-CNRS lab, supervisor: Patrick Paroubek\\
		Thesis: ``Automatic, Adaptive, and Applicative Sentiment Analysis'', project DOXA\\
		Orsay, France
		\vspace{1em}
    } \\
	\parbox[t]{5cm}{
		2007 -- 2009 \\
		M.S. Computer Science
	} &
	\parbox[t]{15cm}{
		Korea Advanced Institute of Science and Technology\\
		Information Systems lab, supervisor: Prof. Chung, Chin-Wan \\
		Thesis: ``An Effective Contextual Advertising using Wikipedia Matching''\\
		Taejon, Republic of Korea
        Graduated with an Excellence Thesis Award
		\vspace{1em}
    } \\
    \parbox[t]{5cm}{
		2003 -- 2007 \\
		B.S. Computer Science
	} &
	\parbox[t]{15cm}{
		Tashkent University of Information Technologies\\
		Tashkent, Uzbekistan
    } \\    
    \end{tabular}
\end{table}

\subsection*{Summer schools}
\begin{itemize}
\item First European Business Intelligence Summer School (eBISS 2011)
\item European Summer School in Logic, Language and Information (ESSLLI 2010)
\end{itemize}

\section*{Publications}

\subsection*{International Journals}

\begin{itemize}

\item Alexander Pak, Delphine Bernhard, Patrick Paroubek, Cyril Grouin, ``A Combined Approach to Emotion Detection in Suicide Notes'' to appear in {\it Biomedical Informatics Insights}

\item Alexander Pak, Chin-Wan Chung, ``A Wikipedia Matching Approach to Contextual
Advertising'' {\it World Wide Web}, 2009. Volume 13, Number 3, 251--274, DOI:
10.1007/s11280-010-0084-2.

\end{itemize}

\subsection*{Domestic Journals}

\begin{itemize}
\item Alexander Pak, Patrick Paroubek, ``Le microblogage pour la microanalyse des
sentiments et des opinions'' {\it Traitement Automatique des Langues}, 2010, vol. 51.3 (pp 75--100).\\
English title: ``Micro blogging for micro sentiment analysis''
\end{itemize}


\subsection*{International conferences}

\begin{itemize}

\item Alexander Pak, Patrick Paroubek, ``Normalization of Term Weights for Sentiment Analysis'' to appear at LTC 2011

\item Alexander Pak, Patrick Paroubek, ``Twitter as a Corpus for Sentiment Analysis and Opinion Mining'', 
{\it LREC 2010. Seventh International Conference on Language Resources and Evaluation}, 
Valetta, Malta: 2010. -6p

\item Patrick Paroubek, Alexander Pak, Djamel Mostefa, ``Annotations for opinion mining evaluation in the industrial context of the DOXA project'', 
{\it LREC 2010. Seventh International Conference on Language Resources and Evaluation}, 
Valetta, Malta: 2010. -6p

\item Alexander Pak, ``Using Wikipedia to Improve Precision of Contextual Advertising'', {\it LTC 2009. Lecture Notes in Computer Science}, 
2011, Volume 6562/2011, 533-543, DOI: 10.1007/978-3-642-20095-3\_49\\
Best Student Paper award

\end{itemize}

\subsection*{Domestic conferences}

\begin{itemize}

\item Alexander Pak, Patrick Paroubek, ``Sentiment Polarity Classification using Dependency Tree Subgraphs Text Representation'' {\it TALN 2011. 18\`eme Conf\'erence sur le Traitement Automatique des Langues Naturelles}, Montpelier, France: 2011. -6p

\item Alexander Pak, Patrick Paroubek, ``Constructing French Affective Lexicon using Twitter'', {\it TALN 2010. 17\`eme Conf\'erence sur le Traitement Automatique des Langues Naturelles}, Montr\'eal, Canada : 2010. - 6p

\end{itemize}

\subsection*{International workshops}

\begin{itemize}

\item Alexander Pak, Delphine Bernhard, Patrick Paroubek, Cyril Grouin, ``Emotion Detection in Clinical Reports. The LIMSI participation in the i2b2 2011/VA
Challenge'' to appear at I2B2, AMIA 2011

\item Alexander Pak, Patrick Paroubek, ``Twitter for Sentiment Analysis: When Language Resources are Not Available,'' DEXA, 2011 {\it 22nd International Workshop on Database and Expert Systems Applications}, Toulouse, France: pp.111--115

\item Alexander Pak, Patrick Paroubek. 2010. ``Twitter Based System: Using Twitter for Disambiguating Sentiment Ambiguous Adjectives''. {\it In Proceedings of the 5th
International Workshop on Semantic Evaluation (SemEval '10). Association for
Computational Linguistics}, Uppsala, Sweden: 436--439

\item Alexander Pak, Patrick Paroubek, ``Text Representation using Dependency Tree
Subgraphs for Sentiment Analysis'', {\it DASFAA 2011. The 16th International Conference on Database Systems for Advanced Applications. In proceedings of Database Systems for Adanced Applications}, Xu J.,Yu G., Zhou S., Unland R., Lecture Notes in Computer Science vol 6637, Hong Kong, China: 2011. 323--332

\end{itemize}

\section*{Talks}

\begin{itemize}

\item Alexander Pak, ``Adaptive Sentiment Analysis'' at Clunch 2011, University of
Pennsylvania, Philadelphia, PA, USA.

\end{itemize}

\section*{Awards and Honors}

\begin{itemize}

\item Best Student Paper award at LTC'09 in Poznan, Poland for paper ''Using Wikipedia to Improve Precision of Contextual Advertising''

\item Excellence Thesis Award at Korea Advanced Institute of Science and Technology

\item First place in Ericsson open student contest for best business idea of SIP application 2006

\item Participation in Google Summer of Code 2006 program

\end{itemize}


\section*{Personal projects}

\begin{itemize}

\item Pyrus: NLP toolkit for Russian in Python3: \url{https://github.com/irokez/Pyrus}
\item 42goals: a simple tool for tracking daily goals: \url{http://42goals.com} \\
(finalist at Mini Seedcamp Weekend in Berlin 2010)
\item Worktrek: online productivity calendar and planning: \url{http://worktrek.com}
\item Irokez CMS: opensource content management system: \url{http://irokez.org}

\end{itemize}

\section*{Technical expertise}
\begin{itemize}
\item Programming languages: Python, C++, JavaScript, PHP
\item Database management systems: MySQL, PostgreSQL, SQLite
\item Markup languages: HTML, XML, LaTeX
\item Operating systems: MS Windows, Linux Debian, Ubuntu
\end{itemize}

\section*{Spoken languages}
\begin{itemize}
\item Russian: native
\item English: fluent (TOEFL iBT score, taken in 2007: 105/110)
\item French: intermediate
\item German, Korean, Chinese: beginner
\end{itemize}

\end{document}
